\cvsection{Experience}

\begin{cventries}

	\cventry
	{Lead Software Engineer} % Job title
	{Koch Ag \& Energy Solutions, LLC} % Organization
	{Wichita, KS, USA} % Location
	{August 2024 -- Present} % Date(s)
	{
		\begin{cvitems}
			\item Design, document, and implement scalable cloud solutions in an
			event-driven Enterprise IT environment with Node.js and Typescript,
			using Serverless Framework with AWS Lambda and related services.
			\item Deliver well-tested, well-documented REST APIs and event consumers
			with OpenAPI and AsyncAPI.
			\item Own my team's technical output, ensuring high-performing,
			supportable solutions that promote reuse.
			\item Identify and implement team processes to deliver high quality work
			consistently.
			\item Refine and prioritize backlog items from a technical perspective.
			\item Manage production incident responses.
		\end{cvitems}
	}

	\cventry
	{Senior Software Engineer} % Job title
	{Very, LLC} % Organization
	{Remote, USA} % Location
	{May 2022 -- April 2024} % Date(s)
	{
		\begin{cvitems}
			\item Saved clients weeks of initial project setup cost by building an
			internal developer platform that scaffolded and deployed tech stacks to
			AWS.
			% \item CI/CD Release Manager for a cross-functional IoT engagement,
			% collaborating daily with data scientists, developers, designers,
			% mechanical/electrical engineers, and key stakeholders on tight
			% deadlines.
			\item Owned CI/CD for a cross-functional team, automating infrastructure
			provisioning and app deployments to AWS with Terraform \& GitHub
			Actions.
			\item Built local-first distributed IoT system for commercial buildings,
			with Elixir/Nerves gateways each managing up to 1000 embedded devices;
			data was synced to cloud Elixir service backed by multi-tenant PostgreSQL
			cluster on AWS.
			\item Architected an IoT video streaming cloud solution on AWS that
			led to a new client engagement.
			% \item Pushed IoT telemetry data to Elixir cloud service via MQTT, AWS IoT
			% Core, and SQS; data was ingested by Broadway and stored in multitenant
			% PostgreSQL cluster with Row-Level Security.
			\item Delivered well-tested, well-documented REST APIs with OpenAPI specs.
			% \item Bundled and delivered polyrepo firmware builds over the air (OTA).
			\columnbreak
			\item Prevented bugs by pioneering an Elixir integration testing framework
			to simulate inter-device communication.
			% \item Successfully advocated for internal adoption.
			% \item Improved time to first deployment across client engagements at Very.
			% \item D1D scaffolded a given tech stack, created and pushed to a
			% GitHub repo, and opened an initial pull request triggering CI/CD workflows
			% deploying to AWS as a friendly introduction for the user.
			% \item Wrote Terraform modules, Cookiecutter templates, and GitHub
			% Actions workflows with a Python/Click CLI.
			% \item Accelerated platform development by securing funding, establishing
			% core team, and getting executive buy-in.
			% \item Tech Lead and Interim Tech Lead for a multimillion dollar client
			% engagement.
			% \item Improved work processes.
			% \item Led internal lecture series on the Nix package manager.
			\item Trained client's new engineering team to take over product
			development at handoff.
			% \item Technologies used: Elixir, AWS, Terraform, PostgreSQL, Docker,
			% Phoenix, Nerves, Python, Django
		\end{cvitems}
	}

	\cventry
	{Software Developer} % Job title
	{Techtronic Industries} % Organization
	{Remote, USA} % Location
	{April 2021 -- May 2022} % Date(s)
	{
		\begin{cvitems}
			\item Improved the customer experience for 572K+ monthly visitors by
			reimplement the Rails backend for ryobitools.com in Elixir/Phoenix,
			resulting in faster performance.
			% \columnbreak
			\item Ensured internal customers could edit web content safely by
			delivering REST APIs with web admin interfaces using Elixir, Phoenix,
			and PostgreSQL.
			\item Safeguarded critical code paths and enabled refactoring by improving
			unit test coverage by 15\% in harttools.com backend.
			% \item Led an initiative to increase automated testing and improve code
			% quality in all backend projects.
			% \item Instigated collaborative GitHub Issues-based workflow to improve
			% coordination between backend and frontend teams.
			\item Improved communication between backend, frontend, and project
			management teams by documenting existing APIs.
			% \item Technologies used: Elixir, Phoenix LiveView, PostgreSQL, JavaScript,
			% HTML/CSS.
		\end{cvitems}
	}

	% \cventry
	% {Co-founder and Co-owner} % Job title
	% {Austinburg Music Academy} % Organization
	% {Cincinnati, OH, USA} % Location
	% {Aug. 2017 -- June 2021} % Date(s)
	% {
	% 	\begin{cvitems}
	% 		\item Designed and conducted successful marketing campaigns with thousands
	% 		of flyers in schools, direct mail, and strategic social media marketing
	% 		through Facebook Ads and Instagram Ads.
	% 		\item Optimized SEO using Google Analytics to become a top contender in
	% 		search results for music lessons in greater Cincinnati area.
	% 		\item Developed a brand presence on Google Business, Facebook, Instagram,
	% 		Yelp, Thumbtack, \& Lessons.com.
	% 		\item Built and maintained Mailchimp lead database.
	% 	\end{cvitems}
	% }

	\cventry
	{Freelance Full-Stack Developer} % Job title
	{Freelance} % Organization
	{Cincinnati, OH, USA} % Location
	{Jan. 2019 -- May 2021} % Date(s)
	{
		\begin{cvitems}
			\item Designed, implemented, and delivered an inventory, customer, and
			sales management web app for retail client using Ruby on Rails.
			% \item Distinguished the product from generic retail competitors by
			% customizing the relational data model to the jewelry domain.
			% \item Technologies used: Ruby on Rails, PostgreSQL, JavaScript, Stimulus
			% Reflex, Bootstrap, Heroku, HTML, CSS.
		\end{cvitems}
	}

\end{cventries}
